\vspace{1.0cm} \LARGE \bf Structured population models demystify MERS-CoV epidemiology

### 2017-05-02 mers-structure.tex
changed to omega notation; added simple model for seasonality

\begin{figure}[h]
 \centering
	\includegraphics[width=0.65\textwidth]{figures/mers_chain.png}
	\caption{\textbf{Tangled chain of MERS-CoV genome and its parts.}
	Tangled chain of the full genome (a), all nucleotides up to position 21000 (b) and all nucleotides past position 21000 (c) of MERS-CoV.
	The same taxa, if available in neighbouring trees, are connected via coloured lines (human sequences in blue, camel sequences in red).
	Tree branches are coloured by inferred ancestral host state (human in grey, camel in black).
	Whilst some of apparent incongruities are caused by having less data in some of the fragments, inconsistencies between topologies occur across internal branches inferred to be in the camel host.
	Human clusters in grey change phylogenetic positions between the trees wholesale, with minor incongruences within clusters.
	This is evidence for recombinant viruses generated in the reservoir entering human populations.
	Coding sequences in the MERS-CoV genome are indicated with arrows at the bottom of the plot with position 21000 indicated by the black line.
	}
	\label{}
\end{figure}

@@

\begin{equation}
r_{j} = \frac{\Gamma(kj+j-1)}{\Gamma(kj)\Gamma(j+1)} \frac{(\frac{R_{0}}{k})^{j-1}}{(1+\frac{R_{0}}{k})^{kj+j-1}}
\end{equation}

>>>>

\begin{figure}[h]
 \centering
	\includegraphics[width=0.65\textwidth]{figures/mers_chain.png}
	\caption{\textbf{Tangled chain of MERS-CoV genome and its parts.}
	Tangled chain of the full genome (a), all nucleotides up to position 21000 (b) and all nucleotides past position 21000 (c) of MERS-CoV.
	The same taxa, if available in neighbouring trees, are connected via coloured lines (human sequences in blue, camel sequences in red).
	Tree branches are coloured by inferred ancestral host state (human in grey, camel in black).
	Whilst some of apparent incongruities are caused by having less data in some of the fragments, inconsistencies between topologies occur across internal branches inferred to be in the camel host.
	Human clusters in grey change phylogenetic positions between the trees wholesale, with minor incongruences within clusters.
	This is evidence for recombinant viruses generated in the reservoir entering human populations.
	Coding sequences in the MERS-CoV genome are indicated with arrows at the bottom of the plot with position 21000 indicated by the black line.
	}
	\label{fig:mers_chain}
\end{figure}

@@

\begin{equation}
p(r = j | R_{0}, \omega) = \frac{\Gamma(\omega j+j-1)}{\Gamma(\omega j)\Gamma(j+1)} \frac{(\frac{R_{0}}{\omega})^{j-1}}{(1+\frac{R_{0}}{\omega})^{\omega j+j-1}}
\end{equation}

\subsubsection*{Introduction seasonality}
We computed the times of camel-to-human introductions in the posterior distribution of trees.
This distribution of introduction times was then discretised as follows: for state  $k = 1, 2, \ldots, L$ in the chain,  $Z_{ijk}$ was $1$ if there as an introduction in month $i$ and year $j$ and $0$ otherwise.
We model the variable $Y_{ij} = \sum_{k = 1}^M Z_{ijk}$ with the hierarchical model:
\begin{align}
 Y_{ij} &\sim \text{Binomial}(L, \theta_{ij}); \\
 logit(\theta_{ij}) &= \alpha_j + \beta_i; \\
 \beta_i &\sim \text{Normal}(0, \sigma_{m}); \\ 
  \sigma_{m} &\sim \text{Cauchy}(0, 2.5); \\
 \alpha_j &\sim \text{Normal}(\mu_{y}, \sigma_{y});  \\
 \mu_{y}  &\sim  \text{Normal}(0, 1); \\
 \sigma_{y} &\sim \text{Cauchy}(0, 2.5).
\end{align}
